On Extending a Full-Sharing Design with Batched Scheduling

### 2015-04-16 paper.tex
removing stuff

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Further Work}
We have presented a simple and novel approach for combining the FS
design with batched scheduling. Experimental results showed that one
average, the extra structures required for the combination do not seem
to have a big impact in the performance. Further work will include
experimentation in more applications and improvements in the PAC
procedure.

>>>>

As we scale the number of threads, for the NS design both scheduling
strategies have similar minimum, average and maximum overhead
ratios. For the FS design, the best minimum overhead ratio is always
for the batched scheduling. For the average and maximum overhead
ratio, local scheduling is always better than batched
scheduling. However, for the average ratio, the results between both
strategies is quite close. For the maximum overhead ratio, the
difference between both strategies is significantly higher.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Further Work}
We have presented a simple and novel approach for combining the FS
design with batched scheduling. Experimental results showed that on
average, the extra structures required for the combination do not seem
to have a big impact in the performance. Further work will include
experimentation in other real world applications.
